\documentclass{article}
\usepackage{amsmath, amssymb}
\usepackage{booktabs}
\usepackage[margin=1in]{geometry}
\usepackage{microtype}
\usepackage{setspace}
\onehalfspacing

\title{Substitution Parameters from Age-Verification Event Studies}
\author{}
\date{}

\begin{document}
\maketitle

\section{Setup}

\paragraph{Goods.} We work with seven goods: six adult content categories ---
PornHub~(PH), xHamster~(XH), xVideos~(XV), XNXX, Chaturbate~(CB), and a
residual Other-XXX bundle~(OXXX) --- plus an outside option~(AO) covering all
other uses of time.  Let $\mathcal{A} = \{\mathrm{PH, XH, XV, XNXX, CB,
OXXX}\}$.  AO is constructed residually:
\[
  m_{\mathrm{AO},t}^m \;=\; 10080 - \sum_{j \in \mathcal{A}} m_{j,t}^m,
\]
where $10080 = 7 \times 24 \times 60$ is the number of minutes in a week.
AO is the ``left-out'' good whose share is pinned by adding-up; we write
equations only for the six adult goods.

\paragraph{Time shares.} The outcome of interest is the time share
\[
  s_i^{mt} \;=\; \frac{m_i^{mt}}{10080},
\]
for machine~$m$, week~$t$, site~$i$.  Because 10080 is total available time
(not total browsing time), the adult shares are small --- $s_A = \sum_{j \in
\mathcal{A}} s_j \ll 1$ --- and AO absorbs nearly all of the budget.  This is a
modeling choice; an alternative denominator is total browsing time, which would
yield a different scaling of the Slutsky parameters but identical diversion
ratios.

\paragraph{Access costs.} Each site carries a shadow access cost $p_i$
incorporating compliance burden, user friction, and voluntary withdrawal.
Age-verification laws raise the access cost of affected sites.  The resulting
change in access cost, $\Delta\ln p_i$, may differ across sites and is not
directly observed; what we observe is the change in usage $\Delta s_i$.

\paragraph{Notation.} $s_0 \equiv s_{\mathrm{AO}} = 1 - s_A$, $s_A \equiv
\sum_{j \in \mathcal{A}} s_j$.

\bigskip

\section{The General Model: AIDS}

\subsection{Specification}

The Almost Ideal Demand System (Deaton and Muellbauer, 1980) relates changes in
time shares to changes in log access costs.  Suppressing the total-time term
--- we treat $T = 10080$ as fixed --- the linearized system is
\begin{equation}\label{eq:aids}
  \Delta s_i \;=\; \sum_{j=1}^{6} \gamma_{ij}\, \Delta \ln p_j,
  \qquad i \in \mathcal{A}.
\end{equation}
The $6 \times 6$ matrix $\Gamma = [\gamma_{ij}]$ is the Slutsky substitution
matrix for time shares.  Three restrictions apply:
\begin{align*}
  \text{Symmetry:}&\quad \gamma_{ij} = \gamma_{ji} \\
  \text{Adding-up:}&\quad \sum_{i=0}^{6} \gamma_{ij} = 0 \quad\forall\, j
    \quad\text{(sum includes AO)} \\
  \text{Homogeneity:}&\quad \sum_{j=1}^{6} \gamma_{ij} = 0 \quad\forall\, i.
\end{align*}
Together these reduce the $6 \times 6$ system to $\binom{6}{2} = 15$ free
parameters.

\subsection{Interpretable objects}

We do \emph{not} normalize the diagonal.  The change in access cost $\Delta\ln
p_j$ for any shocked site $j$ is unobserved, but this is not a problem for
the objects we care about.

\medskip\noindent\textbf{Diversion ratios.}  When site~$j$'s access cost
rises by $\Delta\ln p_j$, site~$j$'s own share falls by $|\gamma_{jj}|
\cdot \Delta\ln p_j$ and site~$i$'s share rises by $\gamma_{ij} \cdot \Delta
\ln p_j$.  The fraction of $j$'s lost share that flows to~$i$ is
\begin{equation}\label{eq:dr}
  DR_{j \to i} \;=\; -\frac{\gamma_{ij}}{\gamma_{jj}}.
\end{equation}
The unknown $\Delta\ln p_j$ cancels.  Slutsky symmetry ($\gamma_{ij} =
\gamma_{ji}$) does \emph{not} imply symmetric diversion ratios:
$DR_{j \to i}/DR_{i \to j} = |\gamma_{ii}|/|\gamma_{jj}|$, which equals one
only when own-price effects are equal.

\medskip\noindent\textbf{Cross-price elasticities.}  $\varepsilon_{ij} =
\gamma_{ij}/s_i$ measures the percentage-point change in site~$i$'s share per
unit increase in $\ln p_j$, normalized by~$i$'s baseline share.

\medskip\noindent\textbf{Allen--Uzawa elasticity.}  $\sigma_{ij} = \gamma_{ij}/
(s_i s_j)$ is a symmetric measure of substitutability; under nested logit it
equals $(1/\lambda - s_0)/s_A$ for pairs in the same nest.

\medskip\noindent Adding-up applies to diversion ratios: summing across all
sites including AO,
\[
  \sum_{i \neq j} DR_{j \to i} + DR_{j \to \mathrm{AO}} \;=\; 1,
\]
so diversion to adult substitutes plus diversion to the outside option sum to
one.  A sum less than one in the data indicates either declining total time
(the fixed-$T$ assumption is violated) or measurement error.

\bigskip

\section{The Simple Model: Nested Logit}

\subsection{Utility and choice probabilities}

We adopt the McFadden (1978) nested logit with two nests: the adult nest
$\mathcal{A}$ and the singleton outside option.  Consumers draw utility
\[
  U_i \;=\; V_i + \varepsilon_i, \qquad i \in \mathcal{A},
  \qquad U_0 \;=\; V_0 + \varepsilon_0,
\]
where the $\varepsilon_i$ for $i \in \mathcal{A}$ follow a generalized extreme
value (GEV) distribution with dissimilarity parameter $\lambda \in (0,1]$.
Standard nested logit yields conditional and marginal share equations:
\begin{equation}\label{eq:within}
  s_{i|A} \;=\; \frac{\exp(V_i/\lambda)}{\displaystyle\sum_{k \in \mathcal{A}}
    \exp(V_k/\lambda)},
  \qquad i \in \mathcal{A},
\end{equation}
\begin{equation}\label{eq:across}
  s_A \;=\; \frac{D_A^\lambda}{1 + D_A^\lambda},
  \qquad
  D_A \;=\; \sum_{k \in \mathcal{A}} \exp(V_k/\lambda).
\end{equation}
The unconditional share is $s_i = s_{i|A} \cdot s_A$.

\subsection{Interpretation of $\lambda$}

$\lambda$ is the \emph{dissimilarity parameter} (also called the nesting
coefficient).  It governs the degree of within-nest correlation in
unobserved utility: lower $\lambda$ means higher correlation and stronger
preference clustering within the adult nest.

\begin{itemize}
  \item $\lambda = 1$: standard multinomial logit.  Independence of irrelevant
    alternatives (IIA) holds globally.  Adult sites substitute for each other
    no more than for non-adult time.
  \item $\lambda \to 0$: within-nest correlation approaches one.  Adult sites
    are nearly perfect substitutes; a shock to one adult site sends almost
    all diverted demand to other adult sites.
  \item $\lambda = 0.217$ (our estimate): strong within-nest preference
    correlation.  Adult sites are substantially closer substitutes for each
    other than for the outside option, but imperfect.
\end{itemize}

Define the composite substitution scalar:
\begin{equation}\label{eq:phi_lambda}
  \varphi_\lambda \;\equiv\; \frac{1}{\lambda} - s_0
  \;\approx\; \frac{1 - \lambda}{\lambda}
  \qquad (\text{since } s_0 \approx 1).
\end{equation}
$\varphi_\lambda$ replaces the $\phi \equiv \sigma_2 - \sigma_1$ combination
from a nested CES.  Like $\phi$, it measures excess within-adult substitution
beyond the IIA baseline: $\varphi_\lambda = 0$ when $\lambda = 1$ (IIA), and
$\varphi_\lambda \to \infty$ as $\lambda \to 0$.

\subsection{Slutsky matrix}

Linearizing the nested logit share equations around the baseline yields the
following Slutsky share derivatives:

\medskip
\begin{center}
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{lll}
  \toprule
  Pair & Formula & Sign ($\lambda < 1$) \\
  \midrule
  $i \neq j$, both $\in \mathcal{A}$ &
    $\displaystyle\gamma_{ij} = \frac{s_i s_j}{s_A}\,\varphi_\lambda$ & $>0$ \\[6pt]
  $i \in \mathcal{A}$, $j = \mathrm{AO}$ &
    $\gamma_{i,0} = s_i s_0$ & $>0$ \\[4pt]
  $i \in \mathcal{A}$ (own price) &
    $\displaystyle\gamma_{ii}
     = -\frac{s_i}{\lambda} + \frac{s_i^2}{s_A}\,\varphi_\lambda$ & $<0$ \\
  \bottomrule
\end{tabular}
\end{center}

\medskip\noindent These satisfy symmetry and adding-up.  The within-adult
cross-price effects $\gamma_{ij}$ have the same $s_i s_j / s_A$ factorization
as in nested CES, with $\varphi_\lambda$ playing the role of $\phi$.

\subsection{Diversion ratios under nested logit}

Applying equation~\eqref{eq:dr} with $i \neq j$, both $\in \mathcal{A}$:
\begin{equation}\label{eq:dr_nl}
  DR_{j \to i} \;=\;
  \frac{(s_i s_j / s_A)\,\varphi_\lambda}
       {(s_j/\lambda) - (s_j^2/s_A)\,\varphi_\lambda}
  \;=\;
  \frac{s_i\,\varphi_\lambda}
       {s_A/\lambda - s_j\,\varphi_\lambda}.
\end{equation}
The numerator is proportional to $s_i$; the denominator does not depend on
$i$.  This yields the same testable proportionality restriction as nested CES:

\medskip
\begin{quote}
  \textbf{Within-adult proportionality.}
  For any $i, k \in \mathcal{A} \setminus \{j\}$,
  \begin{equation}\label{eq:prop}
    \frac{DR_{j \to i}}{DR_{j \to k}} \;=\; \frac{s_i}{s_k}.
  \end{equation}
  Relative diversion from a shutdown of site~$j$ to competing adult sites
  is proportional to their pre-ban time shares.
\end{quote}

\medskip\noindent Equation~\eqref{eq:prop} holds regardless of $\lambda$,
the shock magnitude, or which adult site shuts down.

Diversion to the outside option:
\begin{equation}
  DR_{j \to \mathrm{AO}} \;=\;
  \frac{s_A s_0}{s_A/\lambda - s_j\,\varphi_\lambda}.
\end{equation}
The ratio of total within-adult diversion to outside-option diversion
identifies $\varphi_\lambda$:
\begin{equation}\label{eq:ratio}
  \frac{\displaystyle\sum_{i \neq j,\,i \in \mathcal{A}} DR_{j \to i}}
       {DR_{j \to \mathrm{AO}}}
  \;=\;
  \frac{(s_A - s_j)\,\varphi_\lambda}{s_A s_0}
  \;\approx\;
  \frac{1 - \lambda}{\lambda},
\end{equation}
where the approximation uses $s_0 \approx 1$ and $s_j \ll s_A$.  The
right-hand side involves only the single primitive $\lambda$, directly
identified from the data without knowing shock magnitudes.

\bigskip

\section{Identification Given Simultaneous Shocks}

\subsection{Setup}

Age-verification laws generate three simultaneous access-cost shocks,
each of unknown magnitude:
\begin{enumerate}
  \item \textbf{PH:} PornHub's access cost rises by $\Delta\ln p_{\mathrm{PH}}
    > 0$ (unobserved).
  \item \textbf{XH:} xHamster's access cost rises by $\Delta\ln p_{\mathrm{XH}}
    > 0$ (unobserved), roughly simultaneously with PH.
  \item \textbf{OXXX:} Some sites within the Other-XXX bundle face the same
    mandate; the bundle's effective access cost rises by $\Delta\ln
    p_{\mathrm{OXXX}} > 0$ (unobserved).
\end{enumerate}
All three shocks are of unknown magnitude.  We do not observe the price
changes; we observe only the resulting changes in time shares $\Delta s_i$.
The event study for site $i$ estimates the composite shock:
\begin{equation}\label{eq:obs}
  \Delta s_i
  \;=\; \gamma_{i,\mathrm{PH}} \cdot \Delta\ln p_{\mathrm{PH}}
  \;+\; \gamma_{i,\mathrm{XH}} \cdot \Delta\ln p_{\mathrm{XH}}
  \;+\; \gamma_{i,\mathrm{OXXX}} \cdot \Delta\ln p_{\mathrm{OXXX}}
  \;+\; \varepsilon_i.
\end{equation}
This holds for every site $i \in \mathcal{A} \cup \{\mathrm{AO}\}$, including
the three directly shocked sites.

\subsection{Diversion ratios cancel the unknown shock magnitudes}

Suppose geographic variation allows us to isolate the shock to site $j$:
for states where only $j$ faces the mandate, the event study yields
$\hat\beta_i^j \approx \gamma_{ij} \cdot \Delta\ln p_j$ for each site $i$.
The diversion ratio is then
\begin{equation}\label{eq:dr_estimable}
  \widehat{DR}_{j \to i}
  \;=\; \frac{\hat\beta_i^j}{\left|\hat\beta_j^j\right|}
  \;=\; \frac{\gamma_{ij} \cdot \Delta\ln p_j}
             {|\gamma_{jj}| \cdot \Delta\ln p_j}
  \;=\; \frac{\gamma_{ij}}{|\gamma_{jj}|},
\end{equation}
and $\Delta\ln p_j$ cancels.

\subsection{Problem 1: PH and XH are simultaneously shocked}

If PH and XH are always banned in the same states at the same time, the
event study produces a single combined coefficient $\hat\beta_i^{\mathrm{combined}}
\approx \gamma_{i,\mathrm{PH}} \cdot \Delta\ln p_{\mathrm{PH}} +
\gamma_{i,\mathrm{XH}} \cdot \Delta\ln p_{\mathrm{XH}}$.  We cannot separately
identify the PH and XH columns of the Slutsky matrix; only their
shock-weighted average is estimable.

\medskip\noindent\textit{What nested logit buys here.}  Under nested logit, PH and
XH are in the same nest with the same within-adult proportionality structure.
The ratio of diversion to XV versus XNXX satisfies
$DR_{j \to \mathrm{XV}}/DR_{j \to \mathrm{XNXX}} = s_{\mathrm{XV}}/s_{\mathrm{XNXX}}$
for $j \in \{\mathrm{PH},\mathrm{XH}\}$ --- the same for both shocked sites.
Thus the proportionality test~\eqref{eq:prop} and the identification of
$\lambda$ from equation~\eqref{eq:ratio} remain valid under the combined shock.

\medskip\noindent\textit{What geographic variation buys.}  States that ban
only PH (not XH) and states that ban only XH (not PH) separately identify the
PH and XH columns of the Slutsky matrix.

\subsection{Problem 2: OXXX is simultaneously shocked}

The OXXX shock contaminates the reduced-form coefficients for sites
that didn't face the mandate directly.  Under nested logit,
$\gamma_{i,\mathrm{OXXX}} = (s_i s_{\mathrm{OXXX}}/s_A)\varphi_\lambda$,
which scales with $s_i$ for all $i \in \{$XV, XNXX, CB$\}$.  The OXXX term
therefore adds the same proportional bias to all three non-shocked adult
sites.  Because the ratios $\Delta s_{\mathrm{XV}}/\Delta s_{\mathrm{XNXX}}$
are unaffected by this proportional contamination, the proportionality
test~\eqref{eq:prop} and the ratio in equation~\eqref{eq:ratio} remain valid.
The \emph{level} of $\varphi_\lambda$ (and hence $\lambda$) is, however,
biased upward by OXXX contamination.

\subsection{Summary: what is identified}

\begin{center}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{p{5.1cm} p{4.1cm} p{4.1cm}}
  \toprule
  Object & Without geo.\ variation & With geo.\ variation \\
  \midrule
  Proportionality test $DR_{j\to i}/DR_{j\to k} = s_i/s_k$
  & Yes (nested logit prediction holds under combined shock)
  & Yes \\[4pt]
  Dissimilarity parameter $\lambda$
  & Yes, directly identified (from ratio of within-adult to AO diversion)
  & Yes \\[4pt]
  $\lambda$ in levels (not derived combination)
  & Yes (single primitive, no normalization needed)
  & Yes \\[4pt]
  PH vs.\ XH columns separately (AIDS)
  & No (only shock-weighted sum identified)
  & Yes (PH-only and XH-only states) \\[4pt]
  9 of 15 AIDS parameters
  & No
  & Yes (PH and XH columns via Slutsky symmetry) \\
  \bottomrule
\end{tabular}
\end{center}

\bigskip

\section{Estimation with the Machine-Week Panel}

\subsection{Data structure}

The existing analysis uses a stacked TWFE panel of machine $m \times$
cohort $k \times$ week $t$ observations, with dependent variable
\texttt{win\_min}: winsorized minutes per machine per week, by site.
There are approximately 14.4 million machine-week observations across 14
state cohorts.  For the demand system, we construct
\[
  s_i^{mtk} \;=\; \frac{\texttt{win\_min}_{i,mtk}}{10080},
  \qquad
  s_0^{mtk} \;=\; 1 - \sum_{j \in \mathcal{A}} s_j^{mtk}.
\]

\subsection{Option 1: Two-step minimum distance}

\emph{Step 1.} Run the stacked TWFE event study for each site $j$ separately,
including separate treatment indicators $D_{stk}^j$ for each shocked site
($j \in \{$PH, XH, OXXX$\}$), leveraging geographic variation in which
sites are banned and when.  This yields reduced-form coefficients
$\hat\beta_i^j$ for each outcome site $i$ and each shocked site $j$.

\emph{Step 2.} Compute diversion ratios and structural parameters.
The diversion ratio from $j$ to $i$ follows equation~\eqref{eq:dr_estimable}.
The nested logit identification equation is
\begin{equation}\label{eq:ident}
  \frac{\beta_i}{\beta_{\mathrm{AO}}}
  \;=\; \frac{s_i}{s_A} \cdot \frac{1-\lambda}{\lambda},
\end{equation}
solving directly for $\lambda$:
\begin{equation}\label{eq:lambda}
  \lambda \;=\; \frac{1}{1 + \displaystyle\frac{\beta_i}{\beta_{\mathrm{AO}}}
    \cdot \frac{s_A}{s_i}}.
\end{equation}
The proportionality restriction~\eqref{eq:prop} is
testable by comparing $\hat\beta_i^j/\hat\beta_k^j$ to $s_i/s_k$.

\subsection{Option 2: Seemingly Unrelated Regressions (SUR)}

Stack all six adult site share equations in a joint system:
\begin{equation}\label{eq:sur}
  s_{mtk}^i \;=\; \alpha_{mk}^{i} + \alpha_{tk}^{i}
  + \sum_{j \in \mathcal{S}} \gamma_{ij} \cdot D_{stk}^j
  + \varepsilon_{mtk}^{i},
\end{equation}
where $\mathcal{S} = \{$PH, XH, OXXX$\}$.  Estimate jointly imposing:
\begin{itemize}
  \item \emph{Slutsky symmetry}: $\gamma_{ij}$ in equation $i$ equals
    $\gamma_{ji}$ in equation $j$.
  \item \emph{Nested logit}: $\gamma_{ij} = (s_i s_j/s_A)\,\varphi_\lambda$
    for $i \neq j \in \mathcal{A}$, collapsing the 15-parameter system to
    \textbf{one parameter} $\lambda$ (not two as in nested CES).
\end{itemize}
The SUR uses the full panel variation and allows formal likelihood-ratio or
Wald tests of the nested logit restrictions against the unrestricted AIDS.

\paragraph{Precision from the panel.}  Machine fixed effects $\alpha_{mk}^{i}$
absorb time-invariant taste differences.  Within-machine pre/post
variation is the key signal of substitution.

\paragraph{Heterogeneity across user types.}  The SUR framework provides a
natural common scale for comparing substitution patterns across user groups.
In the SUR, all equations use time shares, so the estimated $\lambda$ and
implied diversion ratios are dimensionless and directly comparable across groups.

\subsection{Heterogeneous nested logit}

Let $g \in \mathcal{G}$ index a person type, and let
$g(m)$ denote the type of machine $m$.  The type-specific SUR is:
\begin{equation}\label{eq:sur_het}
  s_{mtk}^{ig} \;=\; \alpha_{mk}^{ig} + \alpha_{tk}^{ig}
  + \sum_{j \in \mathcal{S}} \gamma_{ij}^g \cdot D_{stk}^j
  + \varepsilon_{mtk}^{ig}.
\end{equation}

Under the type-specific nested logit, the structural Slutsky parameters are:
\begin{equation}\label{eq:nl_het}
  \gamma_{ij}^g \;=\; \frac{s_i^g\, s_j^g}{s_A^g}\,\varphi_\lambda^g,
  \qquad
  \varphi_\lambda^g \;=\; \frac{1-\lambda^g}{\lambda^g},
  \qquad i \neq j \in \mathcal{A},
\end{equation}
where $s_i^g$ is the pre-ban time share for type $g$ and $\lambda^g$ is the
type-$g$ dissimilarity parameter.  The identification equation becomes
\begin{equation}\label{eq:lambda_het}
  \lambda^g \;=\; \frac{1}{1 + \displaystyle\frac{\beta_i^g}{\beta_{\mathrm{AO}}^g}
    \cdot \frac{s_A^g}{s_i^g}},
\end{equation}
directly identifying $\lambda^g$ for each group from existing heterogeneity
event studies and group-specific pre-ban shares.

\paragraph{What the type heterogeneity captures.}  Two sources of
between-type variation enter equation~\eqref{eq:nl_het}:
\begin{enumerate}
  \item \emph{Structural heterogeneity}: $\lambda^g \neq \lambda$.  Different
    types have genuinely different within-nest preference correlation.  Heavy
    users may have lower $\lambda^g$ (stronger within-adult correlation) while
    occasional users have $\lambda^g$ closer to 1.
  \item \emph{Composition heterogeneity}: even if $\lambda^g = \lambda$
    for all $g$, the Slutsky matrix $\Gamma^g$ varies across types because
    baseline shares $s_i^g$ differ.
\end{enumerate}

\paragraph{Testable restrictions.}
\begin{itemize}
  \item $H_0{:}\ \lambda^g = \lambda\ \forall g$ --- dissimilarity parameter
    is homogeneous across types.  Test via Wald test on the interaction of
    $D_{stk}^j$ with type dummies in the SUR.
  \item $H_0{:}\ DR_{j\to i}^g / DR_{j\to k}^g = s_i^g/s_k^g$ ---
    within-adult proportionality holds for type $g$.
\end{itemize}

\paragraph{Example economic hypotheses.}
\begin{itemize}
  \item Heavy past-XXX users likely have low $\lambda^g$: strong preferences
    over the adult nest mean within-adult sites are close substitutes.
  \item Occasional users likely have $\lambda^g$ closer to 1: adult
    consumption is more easily displaced to the outside option.
  \item Users with children in the household may have intermediate $\lambda^g$
    generally with similar within-adult correlation when they do access content.
\end{itemize}

\end{document}
